Software Citation Principles

### 2016-07-25 sc-principles/rebuttal/rebuttal.tex

\item \textbf{Reviewer comment:}
\emph{The use cases described in Section 3 form the main method to answer the implicit research question. Given the importance of these use cases for this paper, I think reference [18] with the details about these use cases should be published in a more official way, either on a site like ArXiv or FigShare, or maybe even as supplemental material or appendix for this paper. I think having these use cases in the appendix of this paper would be the best solution, which would also increase the impact of these use cases and would strengthen the paper in general.}

\textbf{Our response:}
We agree, and have added the full use cases text (with some edits for clarity and completion) as the new Appendix B for completeness.
We also added the comments (with our responses) made publicly following the presentation of the draft principles document at the FORCE2016 confernece, as Appendix C.

\item \textbf{Reviewer comment:}
\emph{As noted above, the logical structure of the paper is unclear, and therefore it is not clear what exactly the main findings are. I think the main findings should be the principles stated in the beginning, and the use cases would then form the main method to arrive at these findings. Alternatively, one could label the principles as ``assumptions'' and apply the use case study to validate these assumptions. In any case, I think the findings are valid but they should be labeled as preliminary, as it is not possible to arrive at a final conclusion for such kinds of questions. Only the future can tell whether software citations really work out.}

\textbf{Our response:}
We agree that the main findings of the paper are the software citation principles, and as described in our response to point 1 above we have updated the introduction and made some structural changes to make this clear.

However, we respectfully disagree that the principles are preliminary, but that they refelct current knowledge and experience.

### 2016-07-26 sc-principles/software-citation-principles.tex
fixed quotation marks
further  editing wording for explanation of historical use case

Possible steps:
\begin{enumerate} \setcounter{enumi}{0}
\item Assume that software developers have created a CITATION file and associated with the source code release/repository.
\item Researcher finds and uses software in the development of new software.
\item Researcher identifies citation metadata file (e.g., ''CITATION'' file) associated with downloaded/installed software source code or in online repository/published location. CITATION file includes necessary citation metadata. CITATION file may include BibTeX entry, suggested citation format.
\item Researcher cites software in source code, documentation, or other metadata-containing file.
\end{enumerate}

@@

Researcher is engaged in historical/cultural research -- e.g., study of video games as cultural artifacts.

@@

Due to overlaps with use case 6, reproducing analysis, we decided not to include
this use case in the table.

>>>>

Possible steps:
\begin{enumerate} \setcounter{enumi}{0}
\item Assume that software developers have created a CITATION file and associated with the source code release/repository.
\item Researcher finds and uses software in the development of new software.
\item Researcher identifies citation metadata file (e.g., ``CITATION'' file) associated with downloaded/installed software source code or in online repository/published location. CITATION file includes necessary citation metadata. CITATION file may include BibTeX entry, suggested citation format.
\item Researcher cites software in source code, documentation, or other metadata-containing file.
\end{enumerate}

@@

Researcher is engaged in historical/cultural research --- e.g., study of video games as cultural artifacts.

@@

This overlaps use case 6 (reproducing analysis), and so we decided not to
include this as a distinct use case.
